### 2018-03-09 Writing/Thesis/content/abstract.tex
integrate first part of comments

% !TEX root = ../my-thesis.tex
%
\pdfbookmark[0]{Abstract}{Abstract}
\chapter*{Abstract}
\label{sec:abstract}
\vspace*{-10mm}

Although the amount of data available worldwide is increasing, the portion of analyzed data remains low. This problem is caused by a lack of experts in the field that are able to carry out an analysis, and the difficulty of the analysis for non-experts. Especially for the task of classification, there are many algorithms with variing performance values from data set to data set - there does not exist one best algorithm, which one can always recommend. One response to this problem is automated machine learning. Therefore, in this thesis, to approaches to construct a ranking of classification algorithms for a new data set, based on properties of that data set,are presented and compared. The first of the two alternatives works on the basis of regression models; one regression model predicts a performance value for each classifier, from which then a ranking is constructed. In contrast, the second, preference based model directly learns and returns rankings. In the evaluation it became clear that the regression based alternative is superior to the preference based approach; the best evaluated regression model, based on the random forest algorithm, achieved values of up to 0.495 for Kendall's rank correlation coefficient and a peformance loss of 1.308 percent on average. However, the tested preference models are superior at least to the baseline in some scenarios. Therefore the conlucion can be drawn that at least certain properties of data sets are connected to performance values of classification algorithms, which can be exploited by regression and preference models, although the regression approach is superior to the preference alternative within the scope of the conducted evaluation.

@@

% Motivation
Die weltweit verfügbare Menge an Daten steigt immer weiter an, und doch bleibt der Anteil der tatsächlich analysierten Daten gering. Dieses Problem entsteht, da nicht genug Experten verfügbar sind, um diese Analyse auszuführen, und es für Laien schwierig ist, das richtige Verfahren auszuwählen. Besonders im Bereich der Klassifikation gibt es viele Algorithmen, deren Performanz jedoch von Datensatz zu Datensatz variieren kann - es gibt also keinen einen besten Algorithmus, der immer eine gute Wahl darstellt. Eine Antwort auf diese Problem ist automatisiertes Machine Learning. Daher werden in dieser Arbeit zwei verschiedene Ansätze, welche für einen neuen Datensatz ein Ranking von Klassifizierungsalgorithmen aufgrund von Eigenschaften des Datensatzes vorhersagt, vorgestellt und miteinander verglichen. Der erste der beiden Ansätze arbeitet auf Grundlage von Regressionsmodellen; ein Ranking wird hier konstruiert indem ein einzelnes Regressionsmodell für jeden Klassifizierungsalgorithmus einen Performanzwert vorhersagt, auf deren basierend dann das Ranking erstellt wird. Der zweite Ansatz beschäftigt sich mit Präferenzmodellen, welche direkt Rankings lernen und zurückgeben. In der Evaluation stellte sich heraus, dass der Regressionsansatz dem Präferenzmodell überlegen ist; das beste der getesteten Regressionsmodelle, basierend auf dem Random Forest Algorithmus, erreicht einen Wert von Kendalls Tau von bis zu 0,495 und Performanzverlustwerte von durchschnittlich nur 1,308 Prozentpunkten. Jedoch sind auch manche der getesten Präferenzmodelle in einigen Punkten wenigstens der zum Vergleich benutzten Baseline überlegen. Daher kann die Schlussfolgerung gezogen werden, dass wenigstens einige der benutzen Eigenschaften der Datensätze mit den Performanzwerten der Klassifizierungsalgorithmen zusammenhängen, und dieser Zusammenhang durch Regressionsmodelle sowohl als auch Präferenzmodelle ausgenutzt werden kann, wobei jedoch der Regressionsansatz letzterem im Rahmen der durchgeführten Evaluation überlegen ist.

>>>>

\pdfbookmark[0]{Abstract}{Abstract}
\chapter*{Abstract}
\label{sec:abstract}
\vspace*{-10mm}

As the demand for machine learning functionality increases dramatically, automated machine learning (AutoML) aims to (partially) automate the creation of machine learning applications. Current AutoML approaches, however, often search for a fitting learning algorithm for a new data set without explicitly considering how properties of the data set might influence algorithm performances. Furthermore, in comparison to recommending a ranking of learning algorithms, this has the disadvantage that no alternatives are presented. Due to a certain inaccuracy of the prediction, these may have an equal or even better performance than the first suggestion regarding the examined data set.

In this thesis, the problem of predicting a ranking of classification algorithms based on properties of a data set is considered. To this end, two approaches are presented and compared. The first uses regression models to predict the accuracy of each classifier on a new data set, and then constructs a ranking from these predictions. Alternatively, a preference-based model directly learns and returns rankings. In an experimental study, it is shown that the regression-based approach performs superiorly to the preference-based alternative. However, the latter still outperforms a static ranking based on how often a classifier has performed best on previously considered data sets.

@@

Da die Nachfrage nach Funktionalität im Bereich des maschinellen Lernens dramatisch ansteigt, hat automatisiertes maschinelles Lernen (AutoML) das Ziel, die Erstellung von Anwendungen im Kontext des maschinellen Lernens (teilweise) zu automatisieren. Aktuelle Ansätze dieser Art suchen jedoch oft nach einem Lernalgorithmus für einen neuen Datensatz, ohne explizit zu berücksichtigen, wie Eigenschaften des Datensatzes die Performanz der Algorithmen beeinflussen können. Außerdem hat dies im Vergleich zu dem Vorschlag eines Rankings von Lernalgorithmen den Nachteil, dass keine Alternativen präsentiert werden. Diese können allerdings, aufgrund der Ungenauigkeit der Vorhersagen, gleichwertig oder sogar bessere Genauigkeiten auf diesem Datensatz haben.

In dieser Arbeit wird das Problem betrachtet, ein Ranking von Klassifizierungsalgorithmen basierend auf den Eigenschaften eines Datensatzes zu erstellen. Dafür werden zwei Ansätze vorgestellt und verglichen. Der erste benutzt Regressionsmodelle,  um die Genauigkeit jedes Klassifizierers für den neuen Datensatz vorherzusagen, und erzeugt dann basierend auf den Vorhersagen ein Ranking. Alternativ lernt ein Präferenzmodell direkt Rankings und gibt sie zurück. In einer experimentellen Studie wird gezeigt, dass der regressionsbasierte Ansatz eine bessere Performanz aufweist als die präferenzbasierte Alternative. Allerdings ist letztere noch einem statischen Ranking überlegen, welches darauf basiert, wie oft ein Klassifizierer die beste Performanz auf zuvor betrachteten Datensätzen hatte.

### 2018-03-09 Writing/Thesis/content/chapter-approach.tex
integrate first part of comments

In general, the aim is to predict a ranking of algorithms based on properties, or meta features of a data set. This means, that as training data for a ranking approach (ranker), a number of performance values of classifiers need to be recorded on data sets in a first pre-processing phase, for which also meta features are to be computed. The table of this collected data is illustrated in Table \ref{tab:performanceValues}, for n meta features, k classifiers and n data sets. This approach to ranking is realized here, as pointed out before, in a regression based and preference based approach, which are explained in detail in the following sections.

\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X | X | X | X | X | X | X}
		%\hline
		MF 1			& MF 2		& ... 	& MF n		& PV 1 		& PV 2 		&	...	&	PV k 		\\ \hline
		$v_{11}$		& $v_{12}$	& ...	& $v_{1n}$	& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ 
		$v_{21}$		& $v_{22}$	& ...	& $v_{2n}$	& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\ 
		...			& ...		& ...	& ...		& ...		& ...		&	...	&	...			\\ 
		$v_{m1}$		& $v_{m2}$	& ... 	& $v_{mn}$	& $p_{2m}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
	\end{tabularx}
	\caption{Training data for the rankers.}
	\label{tab:performanceValues}
\end{table}

\subsection{Regression Based Ranking}
% How is the regression ranking done
One possibility to derive a ranking of classifiers from this information when given a new data set is to use regression models. The idea is to use separate regression models to predict a performance value for each classifier, and to subsequently derive an ordering from these predictions. This is done by splitting the data set compiled beforehand (see Tab. \ref{tab:performanceValues}) into separate data sets that each contain all meta features for all data sets, but only the performance values of one classifier, as illustrated in Table \ref{tab:regressionTables}. The target feature on these individual data sets, the performance value of the classifier, is a numeric value, and thus, a regression model can be trained on each of them. All regression models therefore try to learn the target function \textit{meta features}$\rightarrow$\textit{performance value} for their respective classifier. Hence, for a query instance, after computing the meta features, these are fed into each regression model and the predicted performance value for each classifier is saved. In a second step, the classifiers are ordered according to the predictions. This generation of a ranking is presented in Figure \ref{fig:regression_ranker_model}.

\begin{table}[h]
\centering
\resizebox{\textwidth}{!}{%
	\begin{tabularx}{1.1\textwidth}{X | X | X | X}
		%\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 1	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{11}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{21}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m1}$				\\ \hline\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 2 	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{12}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{22}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m2}$					 
	\end{tabularx}
}	
\vspace{1em}
...
\vspace{1em}	
\resizebox{\textwidth}{!}{%
	\begin{tabularx}{1.1\textwidth}{X | X | X | X}
		%\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value k 	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{1k}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{2k}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{mk}$					 
	\end{tabularx}
}
	\label{tab:regressionTables}
	\caption{How the regression ranker processes the training data.}
\end{table}

@@

\subsection{Preference Based Ranking}
% How is the preference ranking done
The second possibility considered in this context is using preference learning to predict a ranking. Each instance of the data set generated beforehand (see Fig \ref{tab:performanceValues}) contains meta feature information for the considered data set and performance values of all classifiers. Similar to the regression alternative, the performance values can be converted to preference information by sorting the corresponding classifiers by their performance values for each data set. This leads to an ordering of classifiers associated with each instance, and implies that the preference learning task at hand is label ranking. In this case, there exists only one label ranking model which is fed the computed meta data for a new data set and returns an ordering of classifiers, which is depicted in Figure \ref{fig:preference_ranker_model}. Thereby, it attempts to learn the mapping from meta features to an ordering of classifiers directly.

\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X | X | X | X}
		%\hline
		MF 1				& MF 2				& ... 	& MF n				& Ranking 	\\ \hline
		$v_{11}$			& $v_{12}$			& ...	& $v_{1n}$			& $r_1$		\\ 
		$v_{21}$			& $v_{22}$			& ...	& $v_{2n}$			& $r_2$		\\
		...				& ...				& ...	& ...				& ...		\\
		$v_{m1}$			& $v_{m2}$			& ... 	& $v_{mn}$			& $p_m$		 
	\end{tabularx}
	\label{tab:preferenceTable}
	\caption{How the preference ranker processes the training data.}
\end{table}

>>>>

In general, the aim is to predict a ranking of algorithms based on properties, or meta features of a data set. This means, that as training data for a ranking approach (ranker), a number of performance values of classifiers need to be recorded on data sets in a first pre-processing phase, for which also meta features are to be computed. The table of this collected data is illustrated in Table \ref{tab:performanceValues}, for n meta features, k classifiers and m data sets. This approach to ranking is realized here, as pointed out before, in a regression based and preference based approach, which are explained in detail in the following sections.

\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X | X | X | X | X | X | X}
		%\hline
		MF 1			& MF 2		& ... 	& MF n		& PV 1 		& PV 2 		&	...	&	PV k 		\\ \hline
		$v_{11}$		& $v_{12}$	& ...	& $v_{1n}$	& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ 
		$v_{21}$		& $v_{22}$	& ...	& $v_{2n}$	& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\ 
		...			& ...		& ...	& ...		& ...		& ...		&	...	&	...			\\ 
		$v_{m1}$		& $v_{m2}$	& ... 	& $v_{mn}$	& $p_{2n}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
	\end{tabularx}
	\caption{Training data for the rankers.}
	\label{tab:performanceValues}
\end{table}

\subsection{Regression Based Ranking}
% How is the regression ranking done
One possibility to derive a ranking of classifiers from this information when given a new data set is to use regression models. The idea is to use separate regression models to predict a performance value for each classifier, and to subsequently derive an ordering from these predictions. This is done by splitting the data set compiled beforehand (see Tab. \ref{tab:performanceValues}) into separate data sets that each contain all meta features for all data sets, but only the performance values of one classifier, as illustrated in Table \ref{tab:regressionTables}. The target feature on these individual data sets, the performance value of the classifier, is a numeric value, and thus, a regression model can be trained on each of them. All regression models therefore try to learn the target function \textit{meta features}$\rightarrow$\textit{performance value} for their respective classifier. Hence, for a query instance, a new data set, after computing the meta features, these are fed into each regression model and the predicted performance value for each classifier is saved. In a second step, the classifiers are ordered according to the predictions. This generation of a ranking is presented in Figure \ref{fig:regression_ranker_model}.

\begin{table}[h]
\centering
\resizebox{\textwidth}{!}{%
	\begin{tabularx}{1.1\textwidth}{X | X | X | X}
		%\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 1	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{11}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{21}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m1}$				\\ \hline\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 2 	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{12}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{22}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m2}$					 
	\end{tabularx}
}	
\vspace{1em}
...
\vspace{1em}	
\resizebox{\textwidth}{!}{%
	\begin{tabularx}{1.1\textwidth}{X | X | X | X}
		%\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value k 	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{1k}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{2k}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{mk}$					 
	\end{tabularx}
}
	\caption{How the regression ranker processes the training data. Performance data for each classifier are in a separate table, which are then used to train separate regression models.}
	\label{tab:regressionTables}
\end{table}

@@

\subsection{Preference Based Ranking}
% How is the preference ranking done
The second possibility considered in this context is using preference learning to predict a ranking. Each instance of the data set generated beforehand (see Tab. \ref{tab:performanceValues}) contains meta feature information for the considered data set and performance values of all classifiers. Similar to the regression alternative, the performance values can be converted to preference information by sorting the corresponding classifiers by their performance values for each data set. This leads to an ordering of classifiers associated with each instance, and implies that the preference learning task at hand is label ranking. In this case, there exists only one label ranking model which is fed the computed meta data for a new data set and returns an ordering of classifiers, which is depicted in Figure \ref{fig:preference_ranker_model}. Thereby, it attempts to learn the mapping from meta features to an ordering of classifiers directly.

\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X | X | X | X}
		%\hline
		MF 1				& MF 2				& ... 	& MF n				& Ranking 	\\ \hline
		$v_{11}$			& $v_{12}$			& ...	& $v_{1n}$			& $r_1$		\\ 
		$v_{21}$			& $v_{22}$			& ...	& $v_{2n}$			& $r_2$		\\
		...				& ...				& ...	& ...				& ...		\\
		$v_{m1}$			& $v_{m2}$			& ... 	& $v_{mn}$			& $p_m$		 
	\end{tabularx}
	\label{tab:preferenceTable}
	\caption{How the preference ranker processes the training data. The ranker is trained with a table containing meta features and a ranking of classifiers for each data set.}
\end{table}

### 2018-03-09 Writing/Thesis/content/chapter-conclusion.tex
integrate first part of comments

% More evaluation - loss - time & compare agains Jan van Rijn
Furthermore, more insights could be gained about whether this approach is competitive by comparing it with other ranking approaches, for example like the one proposed by \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} \cite{DBLP:journals/ml/AbdulrahmanBRV18}. In this regard it would also be interesting  to implement the loss- and time-loss curves proposed by the authors, which show how loss decreases as one advances in the predicted ranking and tries out the recommended algorithms, and at what cost in the sense of time the sampling of algorithms comes respectively.

@@

% Auto fitting
Depending on the fact whether one is willing to trade off longer build and prediction times for improved accuarcy, it would also be possible to fit more sophisticated regression models for the regression based approach. This could include feature pre-processing, automating the choice of regression algorithm with one of the available tools \cite{thornton2013auto} \cite{feurer2015efficient}, or even using a whole pipeline prediction tool \cite{wever2017automatic} \cite{DBLP:conf/eurogp/SaPOP17}.

>>>>

% More evaluation - loss - time & compare agains Jan van Rijn
Furthermore, more insights could be gained about whether this approach is competitive by comparing it with other ranking approaches, for example like the one proposed by \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} \cite{DBLP:journals/ml/AbdulrahmanBRV18}. In this regard it would also be interesting to implement the loss and time-loss curves proposed by the authors, which show how loss decreases as one advances in the predicted ranking and tries out the recommended algorithms, and at what cost in the sense of time the sampling of algorithms comes respectively.

@@

% Auto fitting
Depending on the fact whether one is willing to trade off longer build and prediction times for improved accuarcy, it would also be possible to fit more sophisticated regression models for the regression based approach. This could include feature pre-processing, automating the choice of regression algorithm with one of the available tools like AUTOWEKA \cite{thornton2013auto} or AUTO-SKLEARN \cite{feurer2015efficient}, or even using a whole pipeline prediction tool, for example ML-Plan \cite{wever2017automatic} or the RECIPE framework \cite{DBLP:conf/eurogp/SaPOP17}.

### 2018-03-09 Writing/Thesis/content/chapter-evaluation.tex
integrate first part of comments

\section{Baseline and Oracle}
% Workings of oracle
In order to evaluate the implemented rankers, their outputs are compared to a perfect output generated by an oracle. The oracle is implemented as a ranker that, after having been trained on a meta data - performance data set returns correct rankings when queried for any instance of that data set. The correct ranking is implied by the performance values (highest first, as the measure used here is predictive accuracy), with ties being handled in a sequential manner, i.e. for the same performance values, the algorithm that was encountered first when constructing the ranking will be ranked before all others with the same value.

@@

% Baseline
Furthermore, we are interested in the question as to what degree knowing about the properties of a data set influences the quality of rankings. Therefore, a ranker that is agnostic of the meta features of a query data set, that is that will always return the same ranking for any data set, is used as a baseline. More specifically, a best algorithm strategy that iteratively determines a ranking by counting the number of data sets where an algorithm is the best choice, is implemented. That means the first algorithm in the best algorithm ranking is the classifier that performs best on most data sets, the second is the best on most data sets when only rankings excluding the first algorithm are considered, and so forth. This baseline is evaluated in the same way as the preference rankers; as it does not predict performance values, the root mean square error of predicted performance values cannot bet computed. Ideally, rankings returned by the preference and regression based rankers should then be statistically significant better than the static baseline, as this would indicate a connection of certain meta features and a performance-induced ranking of classifiers for a data set.

\section{Experimental Setup}
In the following paragraphs, it is briefly summarized under which conditions the experiments which led to the results discussed in the next section were observed. This includes which classifiers and data sets were chosen, and what the specifications of the machines the evaluation was executed on were. It is described how the evaluation was carried out, and which specific regression-based and preference-based implementations where used.

@@

\footnotetext{Data sets that contained the substring 'BNG' in their name for Bayesian Network Generator, which contain data artificially generated by a Bayesian Network \cite{van2014algorithm} for the sake of data stream analysis where not included in the evaluation.}

% How base performance data generated
The performance data of the classifiers for the selected data sets was generated on a linux cluster with nodes consisting of two Intel(R) Xeon(R) E5-2670 processors running at 2.6GHz, 64GB RAM. For the computation of a single performance value of a classifier on a data set, two CPU cores and 16GB RAM were used, with a timeout of eight hours. Up 150 of such processes were executed in parallel. For each of the classifiers, the predictive accuracy (the percentage of correctly classified instances in the data set) was recorded on each data set by means of five times stratified Monte-Carlo cross validation with a 70/30 split in training and test data. The stratified split was generated with the help of JAICore, 'A Java library for infrastructural classes and basic algorithms in the area reasoning, search, and machine learning' [Reference Missing]. When a timeout occurred or the evaluation failed otherwise, the predictive accuracy was set to zero.

@@

% Implementation of measures
For the computation of the Mann-Whitney U and Kendall rank correlation coefficient, Apache Commons implementations were used [REFERENCE MISSING]. Regarding the Mann-Whitney U, the strategy for ties as set to averaging, and the NaNs were set to be removed before the analysis was started.

% How find best version of preference and regression ranker
Furthermore, four alternatives were selected for a regression based and preference based alternative each, to get a general idea of how well the respective approach might be suited for the problem. For the regression based approach, the algorithms chosen were random forest, REPTree, M5P, and linear regression. For all of them, the WEKA implemenation \cite{hall2009weka} was used, and the algorithms where used with the standard hyperparameters set by WEKA. As the preference-based ranking falls under the category of label ranking, and in the jPL-framework, which was used for the implementation of the label ranking algorithms and data set representations, only two alternatives for label ranking are implemented \cite{intelligent2017jpl}, the other two alternatives were generated by modifying the hyperparameters. The implemented alternatives are label ranking by pairwise comparison and instance-based label ranking. As in early tests it became apparent that the instance-based approach might hold more potential, for label ranking by pairwise comparison, only the default configuration dictated by jPL was used. For instance-based label ranking, the default configuration, a configuration where the rank aggregation algorithm used by the label ranker was set to Kemeny-Young, and a configuration with Kemeny-Young rank aggregation and the number of neighbors of the base learner of the label ranker, namely k nearest neighbor (kNN), set to the square root of the number of instances in the training data set. All of the described rankers are included in an overview in Table \ref{tab:methods}. In the following section, these eight variants are compared with the baseline and oracle mentioned in the previous section, and among each others.

@@

Because the ranking itself is implemented as a means of speeding up the process of algorithm selection, the time it takes to rank is not negligible. The full results of how long it takes to build the respective ranking models and how much time they need for predictions can be taken from Table \ref{tab:times}. Results are rounded to the full millisecond, as due to the times being measured with a stop watch in the code, more accurate measurements are not possible. The times for building the regression rankers are not surprising; the regression models take far more time to be built than most of the label ranking methods, most likely due to the fact the regression based rankers have to train 22 regression models in order to be trained themselves. However, it is notable that while the ranking by Pairwise Comparison was not among the best solutions concerning the accuracy of the results, it is the ranker with the highest mean build time for full meta data, and second highest for a reduced meta data set, whereas in other cases the high quality of results is correlated with a high time invested in the building of the ranker. The Random Forest ranker, for example, is the ranker with the highest build time, and also with the rankings of the generally highest quality. But the most important fact to be taken away from Table \ref{tab:times} is that the prediction times for all rankers are short enough to be negligible, with the mean prediction time never being higher than five milliseconds and the maximum never exceeding 50 milliseconds. Furthermore, while the build times are higher, these are not as important due to the fact that each model only needs to be trained once. Although in a real-world scenario, calculation times for meta features also have to be taken into account when ranking, which therefore will be discussed in the following paragraph.

>>>>

\section{Baseline and Oracle}
% Workings of oracle
In order to evaluate the implemented rankers, their outputs are compared to a perfect output generated by an oracle. The oracle is implemented as a ranker that, after having been trained on a meta data-performance data set, returns correct rankings when queried for any instance of that data set. The correct ranking is implied by the performance values (highest first, as the measure used here is predictive accuracy), with ties being handled in a sequential manner, i.e. for the same performance values, the algorithm that was encountered first when constructing the ranking will be ranked before all others with the same value.

@@

% Baseline
Furthermore, we are interested in the question as to what degree knowing about the properties of a data set influences the quality of rankings. Therefore, a ranker that is agnostic to the meta features of a query data set, that is that will always return the same ranking for any data set, is used as a baseline. More specifically, a best algorithm strategy that iteratively determines a ranking by counting the number of data sets where an algorithm is the best choice, is implemented. That means the first algorithm in the best algorithm ranking is the classifier that performs best on most data sets, the second is the best on most data sets when only rankings excluding the first algorithm are considered, and so forth. This baseline is evaluated in the same way as the preference rankers; as it does not predict performance values, the root mean square error of predicted performance values cannot be computed. Ideally, rankings returned by the preference and regression based rankers should then be statistically significantly better than the static baseline, as this would indicate a connection of certain meta features and a performance-induced ranking of classifiers for a data set.

\section{Experimental Setup}
In the following paragraphs, it is briefly summarized under which conditions the experiments which led to the results discussed in the next section were observed. This includes which classifiers and data sets were chosen, and what the specifications of the machines the evaluation was executed on were. It is described how the evaluation was carried out, and which specific regression-based and preference-based implementations were used.

@@

\footnotetext{Data sets that contained the substring 'BNG' in their name for Bayesian Network Generator, which contain data artificially generated by a Bayesian Network \cite{van2014algorithm} for the sake of data stream analysis were not included in the evaluation.}

% How base performance data generated
The performance data of the classifiers for the selected data sets was generated on a linux cluster with nodes consisting of two Intel(R) Xeon(R) E5-2670 processors running at 2.6GHz, 64GB RAM. For the computation of a single performance value of a classifier on a data set, two CPU cores and 16GB RAM were used, with a timeout of eight hours. Up to 150 of such processes were executed in parallel. For each of the classifiers, the predictive accuracy (the percentage of correctly classified instances in the data set) was recorded on each data set by means of five times stratified Monte-Carlo cross validation with a 70/30 split in training and test data. The stratified split was generated with the help of JAICore, \textquotesingle A Java library for infrastructural classes and basic algorithms in the area reasoning, search, and machine learning\textquotesingle [Reference Missing]. When a timeout occurred or the evaluation failed otherwise, the predictive accuracy was set to zero.

@@

% Implementation of measures
For the computation of the Mann-Whitney U and Kendall rank correlation coefficient, Apache Commons implementations were used [REFERENCE MISSING]. Regarding the Mann-Whitney U, the strategy for ties was set to averaging, and the NaNs were set to be removed before the analysis was started.

% How find best version of preference and regression ranker
Furthermore, four alternatives were selected for a regression based and preference based alternative each, to get a general idea of how well the respective approach might be suited for the problem. For the regression based approach, the algorithms chosen were random forest, REPTree, M5P, and linear regression. For all of them, the WEKA implemenation \cite{hall2009weka} was used, and the algorithms where used with the standard hyperparameters set by WEKA. As the preference-based ranking falls under the category of label ranking, and in the jPL-framework, which was used for the implementation of the label ranking algorithms and data set representations, only two alternatives for label ranking are implemented \cite{intelligent2017jpl}, the other two alternatives were generated by modifying the hyperparameters. The implemented alternatives are label ranking by pairwise comparison and instance-based label ranking. As in early tests it became apparent that the instance-based approach might hold more potential, for label ranking by pairwise comparison, only the default configuration dictated by jPL was used. For instance-based label ranking, three different configurations were evaluated, the default configurations and two custom ones. For the first customization, the rank aggregation algorithm used by the label ranker was set to Kemeny-Young. For the second customization, additionally, the number of neighbors of the base learner of the label ranker, namely k nearest neighbor (kNN), was set to the square root of the number of instances in the training data set. All of the described rankers are included in an overview in Table \ref{tab:methods}. In the following section, these eight variants are compared with the baseline and oracle mentioned in the previous section, and among each others.

@@

Because the ranking itself is implemented as a means of speeding up the process of algorithm selection, the time it takes to rank is not negligible. The full results of how long it takes to build the respective ranking models and how much time they need for predictions can be taken from Table \ref{tab:times}. Results are rounded to the full millisecond, as due to the times being measured with a stop watch in the code, more accurate measurements are not possible. The times for building the regression rankers are not surprising; the regression models take far more time to be built than most of the label ranking methods, most likely due to the fact the regression based rankers have to train 22 regression models in order to be trained themselves. However, it is notable that while the ranking by Pairwise Comparison was not among the best solutions concerning the accuracy of the results, it is the ranker with the highest mean build time for full meta data, and second highest for a reduced meta data set, whereas in other cases the high quality of results is correlated with a high time invested in the building of the ranker. The Random Forest ranker, for example, is the ranker with the highest build time (apart from Pairwise Comparison), and also with the rankings of the generally highest quality. But the most important fact to be taken away from Table \ref{tab:times} is that the prediction times for all rankers are short enough to be negligible, with the mean prediction time never being higher than five milliseconds and the maximum never exceeding 50 milliseconds. Furthermore, while the build times are higher, these are not as important due to the fact that each model only needs to be trained once. Although in a real-world scenario, calculation times for meta features also have to be taken into account when ranking, which therefore will be discussed in the following paragraph.
